### 2024-07-02 analysis/analysis.qmd
divided analysis into preprocessing and analysis

This assumes that the data has been parsed from the BibTeX files into table and exported as CSV file.

## Read annotated data

- Update 2024-06-19
- [ ] CA TODO later (if at all): find better way to read in functions

```{r}
require(here)
source(here::here('R/build-df.R'))
source(here::here('R/format-study-results.R'))
source(here::here('R/parse-model-output.R'))
```

- [ ] CA ToDo: Check the warning reported here

```{r}
# get metaMER df:
meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))

# get included studies
included_studies <- meta_df[which(
  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
  dplyr::tibble()

```
### Recoded

```{r}
# get studies re-coded (currently identifiable by presence of bind_field.)
recoded_studies <- included_studies[which(stringr::str_detect(
  included_studies$model_rate_emotion_values,
                                     'bind_field')),]

Maybe limit the verbosity of `get_study_results` below

```{r}
metaMER_results <-
do.call(
  rbind,
    lapply(1:nrow(recoded_studies),
       function(x) get_study_results(recoded_studies[x,])
       )
)

# add unique identifiers

unique_id <- apply(metaMER_results[,c('citekey',
                        'library_id',
                         'model_id',
                         'feature_id',
                         'data_id',
                         'experiment_id')],
                      1, 
                      paste0, 
                      collapse = '-'
) 
metaMER_results$unique_id <- stringr::str_remove_all(unique_id, 
                                                     ' ')

metaMER_results <- metaMER_results |> dplyr::select(unique_id, 
                                 dplyr::everything())

metaMER_results |> dplyr::tibble()

## Summarise annotated data

```{r}
#| eval: true
#| output: asis

print(knitr::kable(table(metaMER_results$citekey,metaMER_results$dimension)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$model_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$feature_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$data_id)))

## Analysis notes

- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [x] Issue 2: We `stimulus_N`
- [x] Issue 3: measure vs statistic?
- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

- [ ] If the _number of stimuli_ varies, divide either to separate experiments or use the largest value (see below for ad-hoc solution).

@@

## Sub-group analysis (based on model type)

```{r}
#| eval: true

# divide models into random forests, SVM and MLR
tmp$model_class_id <- 'MLR/PLS'
tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
table(tmp$model_class_id)
meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")

subgroup.analysis.mixed.effects(x = meta, 
                                subgroups = tmp$model_class_id)
```

@@

>>>>

This assumes that the data has been parsed (`parse-model-output.R`, `format-study-results.R`) and preprocessed (`processing.qmd`).

@@

@@

## Take the max from each study

- Also think of max, median/mean and min?

- Idea: visualise the distributions of the model successes within studies

```{r}
g1 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
  geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
  coord_flip()+
  theme_bw()
g1

# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
# g<-ggplot(S,aes(y=maxvalue))+
#   geom_histogram(bins = 14)+
#   #facet_wrap(.~studyREF)+
#   coord_flip()+
#   theme_bw()
# g
```

## Plot success across the years

```{r}
#| eval: false
g2 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
  geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
  coord_flip()+
  theme_bw()
g2
```
